---
title: "R Notebook"
output: html_notebook
---

# Import dependencies

```{r}
library(tidyverse)
library(here)
library(ggthemes)
library(tidyboot)
```

```{r}
colorblind_pal()(8)
```
"#E69F00","#D55E00","#56B4E9","#009E73","#000000"

# Import data

```{r,message=FALSE}
d.layer.raw <- read_csv(here('results/combined_effect_ave_layer-query-key-value_multihead_albert-xxlarge-v2.csv')) %>%
  separate(pair_id, into = c('prefix', 'pair_id'))

sent_list <- d.layer.raw %>%
  filter((layer_id==0)&(head_id==0)&(pos_type=='context')) %>%
  select(c("pair_id","original_score","cue_type")) %>%
  pivot_wider(names_from="cue_type",values_from="original_score") %>%
  mutate(group_score=str_c(context,verb,sep="-")) %>%
  filter(group_score=="TRUE-TRUE") %>%
  pull("pair_id")
```

How many sentences?

```{r}
d.layer.raw %>% pull(cue_type) %>% unique()
d.layer.raw %>% pull(pair_id) %>% unique()
d.layer.raw %>% pull(pos_type) %>% unique()
```

# 1.1: Report performance

```{r}
d.layer.raw %>%
  #filter(cue_type %in% c('context', 'verb')) %>%
  group_by(cue_type, pair_id) %>%
  summarize(acc = mean(original_score)) %>%
  group_by(cue_type) %>%
  summarize(n = sum(acc))
```

# 4.1: Layer-wise intervention

## Format the data

```{r}
d.layer <- d.layer.raw %>%
  filter(pair_id %in% sent_list) %>%
  filter(cue_type %in% c('context','verb','context_verb')) %>%
  filter(pos_type %in% c('context','verb','options', 'masks', 'rest')) %>%
  mutate(cue_type = replace(cue_type,cue_type=='context_verb','context+verb')) %>%
  mutate(cue_type=factor(cue_type,levels=c('context','verb','context+verb'))) %>%
  mutate(pos_type=factor(pos_type,levels=c('context','verb','options','masks','rest'))) %>%
  mutate(layer_id = layer_id+1)
```

## Main plot for correctly predicted cases

```{r}
d.layer %>%
  group_by(cue_type, layer_id, pos_type, pair_id) %>%
  summarize(effect_ave = mean(effect_ave)) %>%
  group_by(cue_type, layer_id, pos_type) %>%
  tidyboot_mean(effect_ave, nboot = 1000) %>%
  ggplot(aes(x = layer_id, y = empirical_stat, fill = pos_type, color = pos_type, group = pos_type)) +
    geom_line(size=1.2,position = position_dodge(width = 0.4)) +
    geom_ribbon(aes(ymin=ci_lower, ymax=ci_upper), alpha = 0.2, color=NA,) +
    theme_few() +
    scale_color_manual(values=c("#E69F00","#D55E00","#56B4E9","#009E73","#000000")) +
    scale_fill_manual(values=c("#E69F00","#D55E00","#56B4E9","#009E73","#000000")) +
    scale_x_continuous(breaks = c(1,3,5,7,9,11)) +
    labs(x = 'Layer', y ='Effect of intervention') +
    geom_hline(yintercept=0) +
    facet_wrap(~ cue_type, scales="free_y") +
    theme(aspect.ratio = 2,legend.position = 'top', legend.title = element_blank(), 
          axis.text.x=element_text(size=16),axis.text.y=element_text(size=16), axis.title=element_text(size=18),
          strip.text=element_text(size=16), legend.text=element_text(size=16)) 
ggsave('layer.pdf', units = 'in', width = 5, height = 4)
```

## Run stats

```{r}
d.stats <- d.layer %>%
  group_by(cue_type, layer_id, pos_type, pair_id) %>%
  summarize(effect_ave = mean(effect_ave, na.rm = F)) %>% 
  pivot_wider(names_from = pos_type, values_from = effect_ave) %>%
  group_by(layer_id, cue_type) %>%
  summarize(options_p.val = t.test(options)$p.value,
            options_df = t.test(options)$parameter,
            options_stat = t.test(options)$statistic,
            mask_option_diff_p.val = t.test(masks, options, paired = T)$p.value,
            mask_option_diff_stat = t.test(masks, options, paired = T)$statistic) 

d.stats %>% filter(cue_type == 'context')# %>% filter(mask_option_diff_p.val < 0.05/60)
d.stats %>% filter(cue_type == 'verb')
d.stats %>% filter(cue_type == 'context+verb')

```

## Supp plot for incorrectly predicted cases (S1)

```{r}
d.layer %>%
  filter(original_1<0 & original_2>0 & original_1<original_2) %>%
  group_by(cue_type, layer_id, pos_type) %>%
  #summarize(effect_ave = mean(effect_ave)) %>%
  tidyboot_mean(effect_ave, nboot = 1000) %>%
  ggplot(aes(x = as.factor(layer_id), y = empirical_stat, color = pos_type, group = pos_type)) +
    geom_line(size=1.2,position = position_dodge(width = 0.4)) +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width=0.1,size=0.8,linetype='solid',position = position_dodge(width = 0.4)) +
    theme_few() +
    scale_color_manual(values=c("#E69F00","#D55E00","#56B4E9","#009E73","#000000")) +
    labs(x = 'Layer', y ='Effect') +
    geom_hline(yintercept=0) +
    facet_wrap(~ cue_type, scales="free_y") +
    theme(aspect.ratio = 1,legend.position = 'top', legend.title = element_blank(), 
          axis.text.x=element_text(size=10),axis.text.y=element_text(size=14), axis.title=element_text(size=18),
          strip.text=element_text(size=16), legend.text=element_text(size=16)) 

ggsave('layer_split_1_0_2.pdf', units = 'in', width = 9, height = 4)
```

## Supplemental plot for periods and special tokens (S5)

```{r}
d.layer.raw %>%
  filter(pos_type %in% c('period','cls-sep')) %>%
  mutate(cue_type = replace(cue_type,cue_type=='context_verb','context+verb')) %>%
  mutate(cue_type=factor(cue_type,levels=c('context','verb','context+verb'))) %>%
  mutate(pos_type=factor(pos_type,levels=c('period','cls-sep'))) %>%
  mutate(layer_id = layer_id+1) %>%
  filter(original_score) %>%
  group_by(cue_type, layer_id, pos_type) %>%
  #summarize(effect_ave = mean(effect_ave)) %>%
  tidyboot_mean(effect_ave, nboot = 1000) %>%
  ggplot(aes(x = as.factor(layer_id), y = empirical_stat, color = pos_type, group = pos_type)) +
    geom_line(size=1.2,position = position_dodge(width = 0.4)) +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width=0.1,size=0.8,linetype='solid',position = position_dodge(width = 0.4)) +
    theme_few() +
    scale_color_manual(values=c("#0072B2","#CC79A7")) +
    labs(x = 'Layer', y ='Effect') +
    geom_hline(yintercept=0) +
    facet_wrap(~ cue_type, scales="free_y") +
    theme(aspect.ratio = 1,legend.position = 'top', legend.title = element_blank(), 
          axis.text.x=element_text(size=10),axis.text.y=element_text(size=14), axis.title=element_text(size=18),
          strip.text=element_text(size=16), legend.text=element_text(size=16)) +
ggsave('layer_period_cls-sep.pdf', units = 'in', width = 9, height = 4)
```

## Supplemental Figure S4 (cumulative intervention on attention outputs)

In principle, this should be similar to intervening at the residual stream at layer i. 

```{r,message=FALSE}
d.zrep.raw <- read_csv(here('results/combined_effect_ave_all/combined_effect_ave_z_rep_cascade_multihead_albert-xxlarge-v2.csv')) %>%
  separate(pair_id, into = c('prefix', 'pair_id'))

d.zrep <- d.zrep.raw %>%
  filter(pos_type %in% c('options', 'masks','rest')) %>%
  mutate(cue_type = replace(cue_type,cue_type=='context_verb','context+verb')) %>%
  mutate(cue_type=factor(cue_type,levels=c('context','verb','context+verb'))) %>%
  mutate(pos_type=factor(pos_type,levels=c('options','masks','rest'))) %>%
  mutate(layer_id = layer_id+1)

d.zrep %>%
  filter(original_score) %>%
  group_by(cue_type, layer_id, pos_type) %>%
  #summarize(effect_ave = mean(effect_ave)) %>%
  tidyboot_mean(effect_ave, nboot = 1000) %>%
  ggplot(aes(x = as.factor(layer_id), y = empirical_stat, color = pos_type, group = pos_type)) +
    geom_hline(yintercept=0) +
    geom_line(size=1.2,position = position_dodge(width = 0.3)) +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width=0.1,size=0.8,linetype='solid',position = position_dodge(width = 0.3)) +
    theme_few() +
    scale_color_manual(values=c("#56B4E9","#009E73","#000000")) +
    labs(x = 'Layer', y ='Effect') +
    facet_wrap( ~ cue_type, scales="free_y") +
    theme(aspect.ratio = 1,legend.position = 'top', legend.title = element_blank(), 
          axis.text.x=element_text(size=10),axis.text.y=element_text(size=14), axis.title=element_text(size=18),
          strip.text=element_text(size=16), legend.text=element_text(size=16)) 
  
ggsave('zrep.pdf', units = 'in', width = 6, height = 4)
```

# Supplemental figure S2 (same figure for other models)

```{r,message=FALSE}
d.models.raw <- read_csv(here('results/combined_effect_ave_all/combined_effect_ave_layer-query-key-value_multihead_models.csv')) %>%
  separate(pair_id, into = c('prefix', 'pair_id'))

d.models <- d.models.raw %>%
  filter(pos_type %in% c('context','verb','options', 'masks', 'rest')) %>%
  mutate(pos_type=factor(pos_type,levels=c('context','verb','options','masks','rest'))) %>%
  mutate(model=factor(model,levels=c('bert-base-uncased','bert-large-cased','roberta-base','roberta-large',
                                     'albert-base-v2','albert-large-v2','albert-xlarge-v2','albert-xxlarge-v2'))) %>%
  mutate(layer_id = layer_id+1)

d.models %>%
  filter(original_score) %>%
  group_by(model, layer_id, pos_type) %>%
  #summarize(effect_ave = mean(effect_ave)) %>%
  tidyboot_mean(effect_ave, nboot = 1000) %>%
  ggplot(aes(x = as.factor(layer_id), y = empirical_stat, color = pos_type, group = pos_type)) +
    geom_hline(yintercept=0) +
    geom_line(size=1.2,position = position_dodge(width = 0.3)) +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width=0.1,size=0.8,linetype='solid',position = position_dodge(width = 0.3)) +
    theme_few() +
    scale_color_manual(values=c("#E69F00","#D55E00","#56B4E9","#009E73","#000000")) +
    labs(x = 'Layer', y ='Effect') +
    facet_wrap( ~ model, scales="free") +
    theme(aspect.ratio = 1,legend.position = 'top', legend.title = element_blank(), 
          axis.text.x=element_text(size=10),axis.text.y=element_text(size=14), axis.title=element_text(size=18),
          strip.text=element_text(size=16), legend.text=element_text(size=16)) 

ggsave('layer_models.pdf', units = 'in', width = 9, height = 10)
```