---
title: "R Notebook"
output: html_notebook
---

# Import dependencies

```{r}
library(tidyverse)
library(here)
library(ggthemes)
library(tidyboot)
```

# Import data

```{r}
d <- read_csv(here('results/combined_effect_ave_all/combined_effect_ave_layer-query-key-value_multihead.csv')) %>%
  filter(head_id==0) %>%
  separate(pair_id, into = c('prefix', 'pair_id'))
```

How many sentences?

```{r}
d %>% pull(cue_type) %>% unique()
d %>% 
  pull(pair_id) %>%
  unique()
```

# 1.1: Performance

```{r}
d %>%
  #filter(cue_type %in% c('context', 'verb')) %>%
  group_by(cue_type, pair_id) %>%
  summarize(acc = mean(original_score)) %>%
  group_by(cue_type) %>%
  summarize(n = sum(acc))
```

# 1.2: Layer-wise intervention
# Prep the data for plotting
```{r}
d <- d %>%
  mutate(cue_type = replace(cue_type,cue_type=='synonym_1','synonym')) %>%
  mutate(cue_type = replace(cue_type,cue_type=='synonym_2','synonym')) %>%
  mutate(cue_type = replace(cue_type,cue_type=='context_verb','context+verb')) %>%
  mutate(layer_id = layer_id+1)
```

```{r}
d %>%
  filter(original_score) %>%
  filter(pos_type %in% c('options', 'masks')) %>%
  mutate(cue_type=factor(cue_type,levels=c('synonym','context','verb','context+verb'))) %>%
  mutate(pos_type=factor(pos_type,levels=c('options','masks'))) %>%
  group_by(cue_type, layer_id, pos_type) %>%
  #summarize(effect_ave = mean(effect_ave)) %>%
  tidyboot_mean(effect_ave, nboot = 1000) %>%
  ggplot(aes(x = as.factor(layer_id), y = empirical_stat, color = cue_type, group = cue_type)) +
    geom_line(size=1.2) +
    geom_errorbar(aes(ymin=ci_lower, ymax=ci_upper), width=0.1,size=0.8) +
    facet_grid( ~ pos_type) +
    theme_few() +
    scale_color_colorblind() +
    labs(x = 'Layer', y ='Effect') +
    geom_hline(yintercept=0) +
    theme(aspect.ratio = 1,legend.position = 'top', legend.title = element_blank(), 
          axis.text.x=element_text(size=10),axis.text.y=element_text(size=14), axis.title=element_text(size=18),
          strip.text=element_text(size=16), legend.text=element_text(size=16)) +
ggsave('layer.pdf', units = 'in', width = 6, height = 4)
```

```{r}
d.mean <- d %>%
  filter(original_score) %>%
  #filter(cue_type %in% c('context', 'verb')) %>%
  filter(pos_type %in% c('options', 'masks')) %>%
  group_by(original_score, cue_type, layer_id, pos_type) %>%
  tidyboot_mean(effect_ave, nboot = 1)

d %>%
  filter(original_score) %>%
  filter(pos_type %in% c('options', 'masks')) %>%
  group_by(pair_id, cue_type, layer_id, pos_type) %>%
  summarize(effect_ave = mean(effect_ave)) %>%
  mutate(cue_type = fct_relevel(cue_type, c('context', 'verb', 'context_verb'))) %>%
  ggplot(aes(x = as.factor(layer_id), y = effect_ave, color = pos_type, group = pos_type)) +
    geom_line(alpha = 0.1, aes(group = pair_id)) +
    geom_line(aes(y = empirical_stat), data = d.mean) +
    #geom_boxplot(outlier.shape = NA) +
    facet_grid( ~ cue_type) +
    theme_few() +
    theme(aspect.ratio = 1)
```

# Statistical analysis

Run (paired) t-tests at each layer to test where differences between sentence pairs emerge

```{r}
d %>%
  #filter(original_score) %>%
  filter(cue_type %in% c('context', 'verb')) %>%
  filter(pos_type == 'options') %>%
  group_by(pair_id, cue_type, layer_id, pos_type) %>%
  summarize(effect_ave = mean(effect_ave, rm.na = T)) %>%
  spread(cue_type, effect_ave) %>%
  group_by(layer_id) %>%
  summarize(p.val = t.test(context, verb, paired = T)$p.value,
            diff_size = mean(context - verb)) %>%
  mutate(significance_level = case_when(p.val < 0.001 ~ '***', p.val < 0.01 ~ '**', p.val < 0.05 ~ '*', TRUE ~ 'n.s.'))
```

Run single-sample t-tests at each layer to test where differences from 0 emerge

```{r}
d %>%
  filter(cue_type %in% c('context', 'verb')) %>%
  filter(pos_type == 'options') %>%
  group_by(pair_id, cue_type, layer_id, pos_type) %>%
  summarize(effect_ave = mean(effect_ave, rm.na = T)) %>%
  group_by(layer_id, cue_type) %>%
  summarize(p.val = t.test(effect_ave)$p.value) %>%
  mutate(significance_level = case_when(p.val < 0.001 ~ '***', p.val < 0.01 ~ '**', p.val < 0.05 ~ '*', TRUE ~ 'n.s.'))
```


# 1.3: Z-rep intervention (cumulative)

```{r}
d.zrep <- read_csv(here('data/combined_effect_ave_z_rep_cascade_multihead.csv')) 

d.zrep %>%
  filter(original_score) %>%
  filter(pos_type %in% c('options', 'masks')) %>%
  group_by(original_score, cue_type, layer_id, pos_type) %>%
  tidyboot_mean(effect_ave, nboot = 1) %>%
  ggplot(aes(x = as.factor(layer_id), y = empirical_stat, 
             color = pos_type, group = pos_type)) +
    geom_line() +
    #geom_boxplot(outlier.shape = NA) +
    facet_grid( ~ cue_type) +
    theme_few() +
    theme(aspect.ratio = 1)
```


# 1.4: fine-grained analyses

```{r}
d.att <- read_csv(here('results/combined_effect_ave_all/combined_effect_ave_attention.csv'))
d.val <- read_csv(here('results/combined_effect_ave_all/combined_effect_ave_value.csv')) 
```

```{r}
d.head_7 <- d.val %>%
  filter(head_id == 7) %>%
  filter(pos_type=='context')
d.head_44 <- d.att %>%
  filter(head_id == 44) %>%
```

```{r}
d.val %>%
  filter(original_score) %>%
  filter(cue_type == 'context') %>%
  filter(pos_type %in% c('options', 'masks', 'context')) %>%
  group_by(original_score, cue_type, head_id, layer_id, pos_type) %>%
  tidyboot_mean(effect_ave, nboot = 1) %>%
  ggplot(aes(x = as.factor(layer_id), y = empirical_stat, 
             color = pos_type, group = pos_type)) +
    geom_line() +
    #geom_boxplot(outlier.shape = NA) +
    facet_wrap( ~ head_id) +
    theme_few() +
    theme(aspect.ratio = 1)

ggsave('val-heads.pdf', units = 'in', width = 10, height = 12)
```

```{r}
d.att %>%
  filter(original_score) %>%
  filter(cue_type == 'context') %>%
  group_by(original_score, cue_type, head_id, layer_id, pos_type) %>%
  tidyboot_mean(effect_ave, nboot = 100) %>%
  ggplot(aes(x = as.factor(layer_id), y = empirical_stat, 
             color = pos_type, group = pos_type)) +
    geom_line() +
    geom_hline(yintercept = 0, linetype = 'dotted') +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), color = NA, alpha = 0.1) +
    facet_wrap( ~ head_id) +
    theme_few() +
    theme(aspect.ratio = 1)

ggsave('att-heads.pdf', units = 'in', width = 10, height = 12)
```



